Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-11 journal/content.tex
Introduction

--> Introductory paragraph

@@

--> Motivation for research
-- There are no systematic reviews for this
-- A collection of experience reports can be used for creating a theoretical
   base.
--> There is interest in large scale [ref XP13 workshop] \cite{Dingsoyr2013a}

--> Freudenberg, S. and Sharp, H., "The Top 10 Burning Research Questions from
    Practitioners," IEEE Software, pp. 8-9, 2010.

@@

--> This literature review is intended for researchers as a theoretical
   and proven foundation for the real problems that organizations face in
   transformations.
   This is also intended to be directly usable by practitioners, to serve as a
   base of general advice with strong motivation (although every organization
   has unique needs).

@@

Boehm, B. and Turner, R., Balancing Agility and Discipline: A Guide for the
Perplexed: Addison-Wesley, 2003.
Boehm, B., "Get ready for agile methods, with care," IEEE Computer, vol. 35,
pp. 64 - 69, 2002.
--> Size requires more discipline?

>>>>

Software organizations are constantly challenged to function more efficiently,
most often due to the fast evolving software marketplace. Agile methods have
been developed to improve efficiency of software development, but are originally
designed for use in projects of limited size. The benefits of agile are pursued
by large organizations

Despite the

@@

--> Motivation for research
-- There are no systematic reviews for this
-- A collection of experience reports can be used for creating a theoretical
   base.

@@

A number of studies on large scale use of agile exist. However, the studies
present either single cases, do not provide a research method, or does not
provide insights on the adoption aspect of large scale agile development.

* There is interest in large scale [ref XP13 workshop] \cite{Dingsoyr2013a}

* Freudenberg, S. and Sharp, H., "The Top 10 Burning Research Questions from
    Practitioners," IEEE Software, pp. 8-9, 2010.

This literature review is intended for researchers as a theoretical and proven
foundation for the real problems that organizations face in transformations.
This is also intended to be directly usable by practitioners, to serve as a
base of general advice with strong motivation.
%(although every organization has unique needs)

@@

% Boehm, B. and Turner, R., Balancing Agility and Discipline: A Guide for the
% Perplexed: Addison-Wesley, 2003.
% Boehm, B., "Get ready for agile methods, with care," IEEE Computer, vol. 35,
% pp. 64 - 69, 2002.
% --> Size requires more discipline?

This work is organized as follows. In the second chapter we present agile
methods in general, and previous research on adopting agile methods on large
scale. The third chapter discussed the research method used in this work.
The following chapter presents the findings. The final chapter discusses the
results and concludes this work.
